Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-08-10 drafts/outline.tex
tweaked model section

We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration. The key equation in the exponential decay model is
\begin{equation}
    \frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
    \label{eq:model}    
\end{equation}
The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents position along the vertical axis. $k = k_s + k_c$ is the total decay rate of suspended sediment.  $C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed). As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the bed area times the water depth. The volumetric rate at which water passes through a given collector's frontal area is calculated as $ud_ch$. The number of particles passing through this area is found by multiplying by depth-averaged concentration ($N_p = ud_ch\bar{\phi}$). The rate at which particles are removed from suspension by this particular collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$. By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:
\begin{equation}
\frac{d\bar{\phi}}{dt} = \frac{N_c}{V}\frac{dN_p}{dt} = \frac{N_c}{V}\eta^{\prime}ud_ch\bar{\phi} = \eta^{\prime}ud_cI_c\bar{\phi}\,.
\label{eq:collection}
\end{equation}
Please refer to \cite{Fauria_2015} for the full derivation of this model

>>>>

We used a model adapted from \cite{Fauria_2015} to estimate collection efficiency based on exponential decay of suspended sediment concentration. The key equation in the exponential decay model is
\begin{equation}
    \frac{d\bar{\phi}}{dt} = -[\frac{Cv_s}{h}(1-E_r) + \eta^{\prime}ud_cI_c]\bar{\phi}(t) = -k\bar{\phi}(t)\,.
    \label{eq:model}    
\end{equation}
The left and right summands in brackets represent the decay rate of depth-averaged suspended sediment concentration ($\bar{\phi} = \frac{1}{h} \int_0^h\phi(z)dz$) due to settling ($k_s$) and collection ($k_c$) respectively, where $z$ represents position along the vertical axis. $k = k_s + k_c$ is the total decay rate of suspended sediment.  $C$ is a constant based on the shape of the vertical sediment profile, which is assumed to follow the Rouse equation; $v_s$ is the settling velocity; $h$ is water depth; and $E_r$ is the rate of entrainment (i.e., uptake of particle from the channel bed). Please refer to \cite{Fauria_2015} for a detailed derivation of the formula for $k_s$ from established fluid dynamics principles. As for $k_c$, it is derived from flow velocity ($u$), previously described properties of collectors ($\eta^\prime$ and $d_c$), and collector density ($I_c = \frac{N_ch}{V}$), where $N_c$ is number of collectors and $V$ is the fluid volume (i.e., channel bed area times water depth). The volumetric rate at which water passes through a given collector's frontal area is calculated as $ud_ch$. The number of particles passing through this area is found by multiplying by depth-averaged concentration ($N_p = ud_ch\bar{\phi}$). The rate at which particles are removed from suspension by this particular collector is $\frac{dN_p}{dt}=\eta^{\prime}ud_ch\bar{\phi}$. By scaling up to the suite of collectors, modeled identically to one another, the change in concentration due to collection can be derived:
\begin{equation}
\frac{d\bar{\phi}}{dt} = \frac{N_c}{V}\frac{dN_p}{dt} = \frac{N_c}{V}\eta^{\prime}ud_ch\bar{\phi} = \eta^{\prime}ud_cI_c\bar{\phi}\,.
\label{eq:collection}
\end{equation}
